---
title: "NYPD shooting incident data"
author: "Amal Almutairy"
date: "11-10-2020"
output: 
  html_document: 
    theme: journal
    highlight: monochrome
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

```{r}
# packages required
library(dplyr)
library(ggplot2)
library(rsample)
library(recipes)
library(caret)
library(funModeling) 
library(tidyverse) 
library(Hmisc)
library(DT)
```

```
# data source:
# url(https://www.kaggle.com/thaddeussegura/new-york-city-shooting-dataset)
```

## new york city shooting 
List of every shooting incident that occurred in NYC going back to 2006 through the end of the previous calendar year.

Did the NYPD prevent the city from sliding back into the violence of previous eras.
Here’s a look at recent shooting incidents and victims.
The data is supplied by the NYPD.
```{r}
NYPD_shooting <- read.csv("NYPD_Shooting_Incident_Data__Historic_.csv")
```

## NYPD dimention
```{r}
head(NYPD_shooting)
dim(NYPD_shooting)

# omit missing value:
NYPD_shooting <- na.omit(NYPD_shooting)
```
## Number of Deaths
```{r}
STATISTICAL_MURDER_FLAG <- NYPD_shooting$STATISTICAL_MURDER_FLAG 
qplot(STATISTICAL_MURDER_FLAG)
```


## new york city shooting 
```{r}
NYPD_sh=NYPD_shooting %>% select(VIC_RACE, VIC_SEX, VIC_AGE_GROUP, PERP_RACE, OCCUR_TIME, BORO)
NYPD_sh

```

## Plot the frequency of NYPD shooting
```{r}
freq(NYPD_sh)
```

## Plot the frequency of NYPD shooting of the victom race
```{r}
freq(NYPD_sh$VIC_RACE)
freq(NYPD_sh, path_out = ".")
```


